---
title: "Reproducible-research-project1"
output: 
  html_document:
  keed_md: yes
---

## Introduction

It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

##Code for reading in the dataset and/or processing the data
1. Loading of the pachage. Default of the echo will be throughout the document
```{r}
library(knitr)
opts_chunk$set(dev = "png")
```
2. read csv file
```{r}
act = read.csv("/Users/apple/Downloads/activity.csv", na.strings = "NA")
act$date <- as.Date(as.character(act$date, "%Y%m%d"))
summary(act)
```

2. Histogram of the total steps of each day
```{r}
daily_steps_sum <- aggregate(steps ~ date, act, sum, rm.na=TRUE)
str(daily_steps_sum)
hist(daily_steps_sum$steps, xlab = "number of steps", 
     main = "Histogram of the total number of steps taken each day", ylab = "")
```

##Mean and median number of steps taken each day
```{r}
daily_steps_mean <- mean(daily_steps_sum$steps)
daily_steps_med <- median(daily_steps_sum$steps)
```

##Time series plot of the average number of steps taken
1. Average number of steps in 5-minute interval
```{r}
average_steps <- aggregate(steps ~ interval, act, mean, rm.na=TRUE)
str(average_steps)
```

2. Plot of average number of steps taken in 5-minute interval
```{r}
plot(average_steps$interval, average_steps$steps, type = "l", 
     xlab = "Time interval", ylab = "average number of steps taken"
     )
```

##The 5-minute interval that, on average, contains the maximum number of steps
```{r}
max_aveage_steps <- which(average_steps$steps == max(average_steps$steps))
max_steps_interval <- average_steps[max_aveage_steps, "interval"] 
```

##Code to describe and show a strategy for imputing missing data
1.Getting the data structure of the NA value in column steps
```{r}
missing_value <- sum(is.na(act$steps))
Imputed_missing_value <- act
```
2.Assigning the value in each NA steps 
```{r}
for (i in (1: length(Imputed_missing_value$steps))){
  if(is.na(Imputed_missing_value$steps[i])){
    Int <- Imputed_missing_value$interval[i]
    Imputed_missing_value$steps[i] <- 
      average_steps[Int == average_steps$interval, 2]
  }
}
```
##Histogram of the total number of steps taken each day after missing values are imputed
```{r}
sum_imputed_missing_value <- aggregate(steps ~ date, Imputed_missing_value, sum)
hist(sum_imputed_missing_value$steps, xlab = "number of steps", 
     ylab = "", main = "Histogram of the total number of steps taken each day")
```

##Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
1. Identify the weekday and weekend in the date column
```{r}
Imputed_missing_value$weekdays <- weekdays(as.Date(Imputed_missing_value$date))
Imputed_missing_value$weekdays <- ifelse(Imputed_missing_value$weekdays == "Saturday"|Imputed_missing_value$weekdays == "Sunday", "weekend", "weekday")
```
2. Create two dataframes based on weekdays and weekend
```{r}
activity_weekend <- subset(Imputed_missing_value, Imputed_missing_value$weekdays=="weekend")
activity_weekdays <- subset(Imputed_missing_value, Imputed_missing_value$weekdays=="weekday")
```
3. Create the panel plots
```{r}
plot(activity_weekdays$interval, activity_weekdays$steps, main = "Average steps taken 5 minute interval across weekdays"
     , type = "l", col = "blue", xlab = "Interval", ylab = "Step", xlim = c(0,2355), ylim = c(0, 800))
plot(activity_weekend$interval, activity_weekend$steps, main = "Average steps taken 5 minute interval across weekend"
     , type = "l", col = "red", xlab = "Interval", ylab = "Step", xlim = c(0,2355), ylim = c(0, 800))
```
