---
title: "Is an automatic or manual transmission better for MPG"
author: "Stephen Yang"
date: "August 27, 2019"
output: pdf_document
---

# Executive Summary
Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"

First, basic data processing would be used to convert the factor of am to the level of ""automatic" and "manual".
Then we have to differentiate the effect of mpg from two different transmissions by boxplot and use t.test to prove the true difference effect between the two.
Variance inflation provides some clues for giving up the unnecessary variables.
The remaining variables are am, cyl, disp, wt, which finally are to be determined in model selection by anova.

# Data Processing
Load the data from R "dataset". 
Originally the value of am are 0 and 1. We need to transform the binary form into factor.
```{r}
library(ggplot2)
library(car)
data <- mtcars
head(data)
data$am <- factor(data$am)
levels(data$am)<-c("automatic", "manual")
```

# Exploratory analysis
Just take a look at the pvalue. To make sure if transmission type is important to engine performance. 
The boxplot is to demonstrate engine efficiency by different transmissions.
It appears manual transmission shows about 7 mpg more than automatic transmission.
```{r}
t.test(data$mpg[data$am == "automatic"], data$mpg[data$am == "manual"])
boxplot(mpg ~ am, data, main = "Comparison of mpg performance between different transmissions")
am_fit <- lm(mpg ~ am-1, data)
summary(am_fit)$coef
fit <- lm(mpg ~ ., data)
par(mfrow = c(2,2))
plot(fit)
```

# Model Selection
We get to check which variables are influential.
One of the tools is variance inflation and it shows several variables are confounding ,which are am, cyl, disp, wt.
Using anova analysis to check the confounding variables.
So the nested model is a good way to see the sequential testing of coefficients.
As we can see the sequential ANOVA in appendix indicates disp with low value of F statistics which isn't significant. So other variables should be included for final check.
```{r}
test_fit <- lm(mpg ~ am-1, data)
vif(fit)
fit1 <- lm(mpg ~ am+cyl+disp+wt-1, data)
summary(fit1)$coef
```

# Analysis and Conclusion
What if all the confounding variable are all included in the model?
As we can see there's only slight difference over two transmissions.
Manual transmission doesn't show better engine efficiency.
```{r}
final_fit <- lm(mpg ~ am + cyl + wt -1, data)
sum_fit <- summary(final_fit)$coef
Interval <- sum_fit[2,1]+c(-1,1)*qt(.975,final_fit$df)*sum_fit[2,2]
```

# Appendix supporting of model selection
```{r}
test_fit1 <- lm(mpg ~ am + cyl-1, data)
test_fit2 <- lm(mpg ~ am + disp-1, data)
test_fit3 <- lm(mpg ~ am + wt-1, data)
anova(test_fit, test_fit1)
anova(test_fit, test_fit2)
anova(test_fit, test_fit3)
test_fit4 <- lm(mpg ~ am + cyl + wt-1, data)
test_fit5 <- lm(mpg ~ am + cyl + wt + disp-1, data)
anova(test_fit ,test_fit1 ,test_fit4, test_fit5)
```
